### 2023-04-20 writing/manuscript.Rmd
removing old un-used script to avoid confusion

if (full_run == TRUE) {
  source(here("analysis", "builder.R"))
  source(here("analysis", "feature_selection.R"))
  source(here("analysis", "analyses.R"))
  knitr::knit(here("viz", "figures.Rmd"))
} else {
  load(here("results", "preprocessed_data.RData"))
  load(here("results", "lasso_analyses.RData"))
  load(here("results", "analyses.RData"))
}

>>>>

if (full_run == TRUE) {
  source(here("analysis", "builder.R"))
  source(here("analysis", "analyses.R"))
  knitr::knit(here("viz", "figures.Rmd"))
} else {
  load(here("results", "preprocessed_data.RData"))
  load(here("results", "lasso_analyses.RData"))
  load(here("results", "analyses.RData"))
}
